Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

\begin{equation}\label{eq:typerelation}
L_{T1R} \subseteq L_{T2R} \subseteq L_{T3R}
\end{equation}

Where $L_{\text{clone type}}$ is the set of cloned lines found by the rules of the specified clone type.

@@

Where $L_{\text{clone type}}$ is the set of cloned lines found by the rules of the specified clone type. The reason that T2R and T3R are not subsets of T2 and T3, is that T2R and T3R allow variability in method calls which can differ in structure. T2 and T3 do not allow such differences.

@@

None of the surveyed tools had all the desired characteristics. Also, the output of these clone detection tools cannot be post-processed to match the clone definition proposed in Sec.~\ref{sec:research}. This is mainly because the automatically refactorable clones are not necessarily a subset of clones detected by these tools and will thus require an analysis of the entire system.

>>>>

\begin{equation}\label{eq:typerelation}
L_{T1R} \subseteq L_{T2R} \subseteq L_{T3R},
\end{equation}

where $L_{\text{clone type}}$ is the set of cloned lines according to the rules of the respective $\text{clone type}$.

@@

 The reason that T2R and T3R are not subsets of T2 and T3, is that T2R and T3R allow variability in method calls which can differ in structure. T2 and T3 do not allow such differences.

@@

None of the surveyed tools had all the desired characteristics. Also, the output of these clone detection tools cannot be post-processed to match the clone definition proposed in Sec.~\ref{sec:research}. This is mainly because the automatically refactorable clones are not necessarily a subset of the clones detected by these tools (see Sec.~\ref{sec:} and will thus require an analysis of the entire system.
